Topological Equivariant Artist Model

### 2021-12-31 slides/main.tex
functor to mapsto

\subsection{Category Theory}
\begin{frame}{Category $\textcolor{source}{\mathcal{C}}$}
\begin{columns}
    \column{0.39\textwidth}
\begin{equation*}
    \begin{tikzcd}[ampersand replacement=\&]
        \textcolor{source}{C_1} \arrow[r, "f", color=source] \arrow[rd, "g\circ f"', color=source] \arrow["id_{C_1}"', loop, distance=2em, in=215, out=145, color=source] \& \textcolor{source}{C_2} \arrow[d, "g", color=source] \arrow["id_{C_2}"', loop, distance=2em, in=125, out=55, color=source] \\
    \& \textcolor{source}{C_3} \arrow["id_{C_3}"', loop, distance=2em, in=305, out=235, color=source]              
    \end{tikzcd}
    \end{equation*}
    \column{0.59\textwidth}
    \begin{alertblock}{associativity} 
        if $f: C_1 \rightarrow C_2$, $g: C_2 \rightarrow C_3$ and $h: C_3 \rightarrow C_4$ then $h\circ (g \circ f) = (h \circ g) \circ f$
    \end{alertblock}
    \begin{alertblock}{identity} 
        for every $f: C_1 \rightarrow C_2$ there exists identity morphisms $f \circ id_{C_1} = f = id_{C_2} \circ f$
    \end{alertblock}
    \end{columns}
\end{frame}
\begin{frame}{Category $\mathcal{\dbasec}$}
\begin{columns}
    \column{0.49\textwidth}
\begin{equation*}
    \begin{tikzcd}[ampersand replacement=\&]
        \textcolor{source}{C_1} \arrow[r, "f", color=source] \arrow[rd, "g\circ f"', color=source] \arrow["id_{C_1}"', loop, distance=2em, in=215, out=145, color=source] \& \textcolor{source}{C_2} \arrow[d, "g", color=source] \arrow["id_{C_2}"', loop, distance=2em, in=125, out=55, color=source] \\
    \& \textcolor{source}{C_3} \arrow["id_{C_3}"', loop, distance=2em, in=305, out=235, color=source]              
    \end{tikzcd}
    \end{equation*}
    \column{0.49\textwidth}
    \onslide<2-|handout:2->{
    \begin{tikzcd}[ampersand replacement=\&]
            \opensetc_1 \arrow[r, "\iota_{1,2}", color=base] \arrow[rd, "\iota_{1,2}\circ \iota_{2,3}"', color=base] \arrow["id_{\opensetc_1}"', loop, distance=2em, in=215, out=145, color=base] \& \opensetc_2 \arrow[d, "\iota_{2,3}", color=base] \arrow["id_{\opensetc_2}"', loop, distance=2em, in=125, out=55, color=base] \\
        \& \opensetc_3 \arrow["id_{\opensetc_3}"', loop, distance=2em, in=305, out=235, color=base]              
    \end{tikzcd}
    }
    \end{columns}
\end{frame}

@@

\begin{frame}{$\mathcal{C}^{op}$}
    \begin{columns}
        \column{0.29\textwidth}
        \begin{tikzcd}[ampersand replacement=\&]
            \opensetc_1 \arrow[r, "\iota_{1,2}", color=base] \arrow[rd, "\iota_{1,2}\circ \iota_{2,3}"', color=base] \arrow["id_{\opensetc_1}"', loop, distance=2em, in=215, out=145, color=base] \& \opensetc_2 \arrow[d, "\iota_{2,3}", color=base] \arrow["id_{\opensetc_2}"', loop, distance=2em, in=125, out=55, color=base] \\
        \& \opensetc_3 \arrow["id_{\opensetc_3}"', loop, distance=2em, in=305, out=235, color=base]              
    \end{tikzcd}
        \column{0.69\textwidth}
        \onslide<2-|handout:2->{
            \begin{tikzcd}[ampersand replacement=\&]
            \cgamma{\opensetc_1}{\dtotalc\restriction_{\opensetc_1}} \&  \& \cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}} \arrow[ll, "\iota^*\restriction_{\opensetc_1}"', color=set]\\
            \&\&\\\&  \& \cgamma{\opensetc_3}{\dtotalc\restriction_{\opensetc_3}} \arrow[uu, "\iota^*\restriction_{\opensetc_2}"', color=set] \arrow[lluu, "\iota^*\restriction_{\opensetc_2} \circ \iota^*\restriction_{\opensetc_1}", color=set]
            \end{tikzcd}

@@

\begin{frame}{Functor $\textcolor{functor}{\bm{F}}: \textcolor{source}{\mathcal{C}} \rightarrow \textcolor{target}{\mathcal{D}}$}
\begin{columns}
    \column{.39\textwidth}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&, ]
            \onslide*<1-|handout:1->{\textcolor{source}{c}} 
            \onslide*<1-|handout:1->{\arrow[d, "f"', shift right=0, color=source]} \onslide*<3-|handout:3->{\arrow[r, "F", color=functor]} \& 
            \onslide*<2|handout:2>{\textcolor{target}{d}}
            \onslide*<3-|handout:3->{\textcolor{target}{F(c)}} 
            \onslide*<2|handout:2>{\arrow[d, shift right=0, color=target]}
            \onslide*<3-|handout:3->{\arrow[d, "F(f)", shift right=0, color=target]} \\
            \onslide*<1-|handout:1->{\textcolor{source}{c^{\prime}}} 
            \onslide*<3-|handout:3->{\arrow[r, "F"', color=functor]}\& 
            \onslide*<2|handout:2>{\textcolor{target}{d^{\prime}}}
            \onslide*<3-|handout:3->{\textcolor{target}{F(c^{\prime})}}                      
        \end{tikzcd}
    \end{equation*}
    \column{.59\textwidth}
    \begin{alertblock}<4-|handout:4->{composition}
    $\textcolor{functor}{F}(\textcolor{source}{g}) \circ  \textcolor{functor}{F}(\textcolor{source}{f}) = \textcolor{functor}{F} (\textcolor{source}{g}\circ \textcolor{source}{f})$
    \end{alertblock}
    \begin{alertblock}<5-|handout:5->{identity}
    $\textcolor{functor}{F}(\textcolor{source}{id_c}) = \textcolor{target}{id}_{\textcolor{functor}{F}(\textcolor{source}{c})}$
    \end{alertblock}
\end{columns}
\end{frame}

>>>>

\subsection{Category Theory}

\begin{frame}{Category $\textcolor{source}{\mathcal{C}}$}
\begin{columns}
    \column{0.39\textwidth}
    \begin{equation*}
    \begin{tikzcd}[ampersand replacement=\&]
        \onslide*<1-|handout:1>{\textcolor{source}{C_1}} 
        \onslide*<3-|handout:1>{\arrow[r, "f", color=source]}
        \onslide*<4-|handout:1>{\arrow[rd, "g\circ f"', color=source]}
        \onslide*<2-|handout:1>{\arrow["id_{C_1}"', loop, distance=2em, in=215, out=145, color=source]} \& 
        \onslide*<1-|handout:1>{\textcolor{source}{C_2}}
        \onslide*<3-|handout:1>{\arrow[d, "g", color=source]} 
        \onslide*<2-|handout:1>{\arrow["id_{C_2}"', loop, distance=2em, in=125, out=55, color=source]} \\\& 
        \onslide*<1-|handout:1>{\textcolor{source}{C_3}}
        \onslide*<2-|handout:1>{\arrow["id_{C_3}"', loop, distance=2em, in=305, out=235, color=source]}              
    \end{tikzcd}
    \end{equation*}
    \column{0.59\textwidth}
    \begin{alertblock}<5-|handout:1>{associativity} 
        if $f: C_1 \rightarrow C_2$, $g: C_2 \rightarrow C_3$ and $h: C_3 \rightarrow C_4$ then $h\circ (g \circ f) = (h \circ g) \circ f$
    \end{alertblock}
    \begin{alertblock}<6-|handout:1>{identity} 
        for every $f: C_1 \rightarrow C_2$ there exists identity morphisms $f \circ id_{C_1} = f = id_{C_2} \circ f$
    \end{alertblock}
    \end{columns}
\end{frame}

\begin{frame}{Category $\mathcal{\dbasec}$}
\begin{columns}
    \column{0.49\textwidth}
\begin{equation*}
    \begin{tikzcd}[ampersand replacement=\&]
        \textcolor{source}{C_1} \arrow[r, "f", color=source] \arrow[rd, "g\circ f"', color=source] \arrow["id_{C_1}"', loop, distance=2em, in=215, out=145, color=source] \& \textcolor{source}{C_2} \arrow[d, "g", color=source] \arrow["id_{C_2}"', loop, distance=2em, in=125, out=55, color=source] \\
    \& \textcolor{source}{C_3} \arrow["id_{C_3}"', loop, distance=2em, in=305, out=235, color=source]              
    \end{tikzcd}
    \end{equation*}
    \column{0.49\textwidth}
    \onslide<2-|handout:1>{
    \begin{tikzcd}[ampersand replacement=\&]
            \opensetc_1 \arrow[r, "\iota_{1,2}", color=base] \arrow[rd, "\iota_{1,2}\circ \iota_{2,3}"', color=base] \arrow["id_{\opensetc_1}"', loop, distance=2em, in=215, out=145, color=base] \& \opensetc_2 \arrow[d, "\iota_{2,3}", color=base] \arrow["id_{\opensetc_2}"', loop, distance=2em, in=125, out=55, color=base] \\
        \& \opensetc_3 \arrow["id_{\opensetc_3}"', loop, distance=2em, in=305, out=235, color=base]              
    \end{tikzcd}
    }
    \end{columns}
\end{frame}

@@

\begin{frame}{$\mathcal{C}^{op}$}
    \begin{columns}
        \column{0.29\textwidth}
        \begin{tikzcd}[ampersand replacement=\&]
            \opensetc_1 \arrow[r, "\iota_{1,2}", color=base] \arrow[rd, "\iota_{1,2}\circ \iota_{2,3}"', color=base] \arrow["id_{\opensetc_1}"', loop, distance=2em, in=215, out=145, color=base] \& \opensetc_2 \arrow[d, "\iota_{2,3}", color=base] \arrow["id_{\opensetc_2}"', loop, distance=2em, in=125, out=55, color=base] \\
        \& \opensetc_3 \arrow["id_{\opensetc_3}"', loop, distance=2em, in=305, out=235, color=base]              
    \end{tikzcd}
        \column{0.69\textwidth}
        \onslide<2-|handout:1>{
            \begin{tikzcd}[ampersand replacement=\&]
            \cgamma{\opensetc_1}{\dtotalc\restriction_{\opensetc_1}} \&  \& \cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}} \arrow[ll, "\iota^*\restriction_{\opensetc_1}"', color=set]\\
            \&\&\\\&  \& \cgamma{\opensetc_3}{\dtotalc\restriction_{\opensetc_3}} \arrow[uu, "\iota^*\restriction_{\opensetc_2}"', color=set] \arrow[lluu, "\iota^*\restriction_{\opensetc_2} \circ \iota^*\restriction_{\opensetc_1}", color=set]
            \end{tikzcd}

@@

\begin{frame}{Functor $\textcolor{functor}{\bm{F}}: \textcolor{source}{\mathcal{C}} \rightarrow \textcolor{target}{\mathcal{D}}$}
\begin{columns}
    \column{.39\textwidth}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&, ]
            \onslide*<1-|handout:1>{\textcolor{source}{c}} 
            \onslide*<1-|handout:1>{\arrow[d, "f"', shift right=0, color=source]} 
            \onslide*<3-|handout:1>{\arrow[r, "F", color=functor, maps to]} \& 
            \onslide*<2-3|handout:0>{\textcolor{target}{d}}
            \onslide*<4|handout:0>{\textcolor{target}{F(c)}} 
            \onslide*<0|handout:1>{\textcolor{target}{F(c)=d}} 
            \onslide*<2|handout:1>{\arrow[d, shift right=0, color=target]}
            \onslide*<3-|handout:1>{\arrow[d, "F(f)", shift right=0, color=target]} \\
            \onslide*<1-|handout:1>{\textcolor{source}{c^{\prime}}} 
            \onslide*<3-|handout:1>{\arrow[r, "F"', color=functor, maps to]}\& 
            \onslide*<2-3|handout:0>{\textcolor{target}{d^{\prime}}}
            \onslide*<4-|handout:0>{\textcolor{target}{F(c^{\prime})}}
            \onslide*<0|handout:1>{\textcolor{target}{F(c^{\prime})= d^{\prime}}}                    
        \end{tikzcd}
    \end{equation*}
    \column{.59\textwidth}
    \begin{alertblock}<5-|handout:1>{composition}
    $\textcolor{functor}{F}(\textcolor{source}{g}) \circ  \textcolor{functor}{F}(\textcolor{source}{f}) = \textcolor{functor}{F} (\textcolor{source}{g}\circ \textcolor{source}{f})$
    \end{alertblock}
    \begin{alertblock}<6-|handout:1>{identity}
    $\textcolor{functor}{F}(\textcolor{source}{id_c}) = \textcolor{target}{id}_{\textcolor{functor}{F}(\textcolor{source}{c})}$
    \end{alertblock}
\end{columns}
\end{frame}
